--- 
title: "Analisis Cluster dengan R"
author: "Deden Istiawan"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
colorlinks: yes
lot: yes
lof: yes
papersize: a4
fontsize: 10pt
graphics: yes
mathspec: true
geometry:
  - tmargin=2.5cm
  - bmargin=2.5cm
  - lmargin=3.0cm
  - rmargin=2.0cm
github-repo: dedenistiawan/clustering
description: "Analsis Cluster dengan Menggunakan Pemrograman R"
---

# Pengantar {-}
```{=html}
<style>
body{
text-align: justify}
</style>
```
> A Markdown-formatted document should be publishable as-is, as plain text, without looking like it’s been marked up with tags or formatting instructions.  
> 
> --- John Gruber


Jika ada pertanyaan, kritik dan saran, atau diskusi ketika Anda menemukan error saat Anda mencoba program dalam buku ini, Anda dapat mengirimkannya melalui email ke deden.istiawan@itesa.ac.id dengan subject email “Analisis Cluster dengan R”.

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
